---
title: "Presentation Ninja"
subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Yihui Xie"
  - "Garrick Aden-Buie"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

---

# Julie Intro - 4 min
# The problem (slide)

---

# Star Wars slides

## ROpenSci, RLadies, RStudio, Mozilla on the hands?

---

# Open science as a movement

---

# Creative contributions help people feel more included 

Get paper to cite on this (STEM inclusive pedagogy)

---

# Allison: story about Openscapes opening the art door or something (3 min)

---

---

---

# Julie: Openscapes momentum

What is Openscapes Champtions & why is it so impactful & different (e.g. length, teams, etc.)

---

(Zoom faces & logos)

---

Examples of what we talk about 

- R Markdown
- Onboarding docs & Codes of Conduct
- Anti-racism & inclusion

---

## Allison Openscapes experience 

### 3 minutes (3 slides?)

- How it's impacted me, my teaching, how I feel working in data science

---

- Ripple effect of Openscapes impacts 

---

- Scaling out impact? 

- Value in confidence building 

- A community at UCSB

- End on growth & ripple effect here, leading into Julie's section on learning & iterating

---

# Julie: we're learning & iterating (3 minute section)

- Learning w/ Tara & Dawn
- Putting kinder science up from (not hidden behind DS)
- Artwork is a part of our grants
- Also investing in DEI (line item in grants, etc.)

---

# Learning & iterating represented in artwork (Allison - 2 min)

- Doodles > Sketches > Drafts > Final
- How this captures changes in Openscapes? 
- tidydata series?

---

# Closing - Julie (2 min)

- Have pathways illustration as the background
- 


---
